Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2021-07-20 paper/paper.tex
WIP. About to Change graph_layout::c again

\subsection*{Chemoaffinity model}

\subsubsection*{Wildtype}

First, we describe the behaviour of a model which has only the gradient-based
chemoaffinity effect and no axon-axon interaction or border effect
(i.e.~$m_2=m_3=0$). This model was run with $n=8$ branches per RGC axon. All
receptor-ligand signals induced repulsive interactions (i.e.~gradient
descent). Receptor and ligand expressions were as shown in Fig.\,\ref{f:ex},
noting that tectal ligand expression was of exponential form
(Eq.\,\ref{e:tecexp}). Fig.\,\ref{f:ch}A gives a colour map of retinal
ganglion cell soma locations, with the colour red encoding $x$ position on the
temporal-nasal axis (with red signifying nasal positions). Green encodes $y$
position on the dorso-ventral axis.
%
Fig.\,\ref{f:ch}B shows the expected final location of each RGC axon,
according to experimental observations, in a `fishnet' plot which draws lines
between adjacent axons giving a visual indication of the topology of the
arrangement.
%
Fig.\,\ref{f:ch}C shows the position of
400 branches at $t=500$ (in arbitrary time units). Considering each
coordinate axis separately, each branch interacts differentially with two
opposing gradients. Branches which settle nearest the rostral edge of the
tectum interact more strongly with the gradient $L_0$ than with $L_2$
(Fig\,\ref{f:ex}C). A similar pair of gradients separate branches along the
M-L tectal axis. The branches become positioned on a grid due to the
discretization of the tectal ligand gradient (as the number of branches and
tectal elements tends towards infinity, the arangement tends towards a
continuous map---see Fig.\,S1 \textbf{FIXME}).

\begin{figure}
\includegraphics[width=\linewidth]{./images/fig_chemo.png}
\caption{Chemoaffinity model}
\label{f:ch}
\end{figure}

@@

\subsubsection*{Tectal ablation etc}

\subsection*{Chemoaffinitiy with axon-axon interaction}

\subsubsection*{Wildtype}
\subsubsection*{Tectal ablation etc}

>>>>

\begin{figure}
\includegraphics[width=\linewidth]{./images/j4_ee_wt.png}
\caption{Gradient following model with axon-axon interaction}
\label{f:wt}
\end{figure}

We first present the result of running the model above, which assumes that
axonal growth cones express graded levels of receptors which interact with
ligands expressed as gradients on the tectum and on the surface of other
growth cones to guide their movement. We make the following additional
assumptions: i) All receptor-ligand interactions are repulsive, as for
EphA-ephrinA coupling \citep{nakamoto_topographically_1996}; and ii) tectal
ligand expressions vary exponentially along a given axis, following
Eq.\,\ref{e:tecexp}.

\subsection*{Chemoaffinity---Wildtype}

Introductory sentence.

We now describe the behaviour of a model which has only the gradient-based
chemoaffinity effect and no axon-axon interaction or border effect
(i.e.~$m_2=m_3=0$). This model was run with $n=8$ branches per RGC axon. All
receptor-ligand signals induced repulsive interactions (i.e.~gradient
descent). Receptor and ligand expressions were as shown in Fig.\,\ref{f:ex},
noting that tectal ligand expression was of exponential form
(Eq.\,\ref{e:tecexp}). Fig.\,\ref{f:ch}A gives a colour map of retinal
ganglion cell soma locations, with the colour red encoding $x$ position on the
temporal-nasal axis (with red signifying nasal positions). Green encodes $y$
position on the dorso-ventral axis.
%
Fig.\,\ref{f:ch}B shows the expected final location of each RGC axon,
according to experimental observations, in a `fishnet' plot which draws lines
between adjacent axons giving a visual indication of the topology of the
arrangement.
%
Fig.\,\ref{f:ch}C shows the position of
400 branches at $t=500$ (in arbitrary time units). Considering each
coordinate axis separately, each branch interacts differentially with two
opposing gradients. Branches which settle nearest the rostral edge of the
tectum interact more strongly with the gradient $L_0$ than with $L_2$
(Fig\,\ref{f:ex}C). A similar pair of gradients separate branches along the
M-L tectal axis. The branches become positioned on a grid due to the
discretization of the tectal ligand gradient (as the number of branches and
tectal elements tends towards infinity, the arangement tends towards a
continuous map---see Fig.\,S1 \textbf{FIXME}).

\begin{figure}
\includegraphics[width=\linewidth]{./images/j4_ee_chemoonly_wt_chemoonly.png}
\caption{Chemoaffinity model}
\label{f:ch}
\end{figure}

@@
